Metal Mixing and Ejection in Dwarf Galaxies is Dependent on Nucleosynthetic Source

### 2018-07-31 main.tex
commenting out duplicate section in 3.1 from weird merge conflict

\begin{abstract}
Using a high resolution simulation of an isolated dwarf galaxy, accounting for multi-channel
stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy by galactic winds. For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal and power-law distribution. The log-normal component generally describes gas at lower metal fractions undergoing enrichment towards the mean metal fraction, driven by recent enrichment events in the power-law tail. The PDF properties, and relative significance of these two components, vary within each ISM phase. Hot gas is dominated by recent enrichment, with a significant power-law tail to high metal fractions, while cold gas is dominated by the log-normal component. In addition, elements dominated by asymptotic giant branch (AGB) wind enrichment, such as N and Ba, mix less efficiently than elements dominated by supernova enrichment, such as $\alpha$ elements and Fe. This difference is driven by the differences in
%mm energetics between each source, particularly the poor coupling of AGB winds to the ISM.
    source locations, particularly the higher chance compared to massive stars for AGB stars to eject material into cold gas.
Nearly all of the produced metals are ejected from the galaxy (only 4\% are retained), but metals dominated by AGB enrichment are retained at a fraction of 20\%. In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread compared to elements synthesized in either core collapse or Type Ia supernovae. We discuss the observational implications of these results, their potential use in developing improved models of galactic chemical evolution, and their generalization to more massive galaxies.
\end{abstract}

@@

The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain. We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (HIM T$\ge 10^{5.5}$~K), and locked in stars (yellow). Again, with the exception of H and He, we only consider metals produced self-consistently through our star formation and stellar feedback methods; the initial mass of each metal species is zero.

We find two major results. First, nearly all of the metals reside within neutral gas, mostly in the CNM; only a few percent reside in the hot phases. The exact fraction varies with each species, most notably for carbon; these fluctuations are at most $\sim 10$\%. This is not surprising, as the cold phases represent the majority of the mass in the ISM, but, as shown in Section~\ref{sec:statistics}, even though the cold phases harbor most of the metals, the hot phases have significantly higher metal mass fractions. Second, only a small fraction of produced metals are retained within the dwarf galaxy, in agreement with observations of nearby dwarf galaxies \citep[see][]{Kirby2011-metals, McQuinn2015}; however, the retention factor varies. The top panel shows a qualitative disagreement between the retention fractions of N and Ba (about 20\% for each) as compared to the rest of the metals ($\sim$ 4 -- 5\%). This suggests that individual metals \textit{do not} share the same dynamical evolution. Clearly, metal enrichment in galaxies is a phenomenon that cannot be fully captured using single, global metallicity field. In this particular case, assuming that all metals behave the same would underestimate the N and Ba enrichment by a factor of up to five, at least for low mass dwarf galaxies.
%mm [end of apparently deleted section] >>>>>>> 134a2fabac2aea2275cb3e8014308282b438742f

@@

%mm [you could cut this if you want.]
     It is worth noting that this PDF shows the rather small cold gas 
     fraction found in these models in comparison to the Milky Way
      ISM, where roughly half the mass is found in cold gas 
      \citep{Ferriere2001}.
Finally, \cite{Hopkins2013} suggests a different functional form for describing these PDFs across a range of idealized simulations, but it still may be insufficient to fully describe the density PDF in realistic galaxy simulations. Clearly, we are far from a general understanding of mass-weighted and volume-weighted density PDFs in the case of a turbulent, self-gravitating, multi-phase ISM.

>>>>

\begin{abstract}
Using a high resolution simulation of an isolated dwarf galaxy, accounting for multi-channel
stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy by galactic winds. For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal and power-law distribution. The log-normal component generally describes gas at lower metal fractions undergoing enrichment towards the mean metal fraction, driven by recent enrichment events in the power-law tail. The PDF properties, and relative significance of these two components, vary within each ISM phase. Hot gas is dominated by recent enrichment, with a significant power-law tail to high metal fractions, while cold gas is dominated by the log-normal component. In addition, elements dominated by asymptotic giant branch (AGB) wind enrichment, such as N and Ba, mix less efficiently than elements dominated by supernova enrichment, such as $\alpha$ elements and Fe. This difference is driven by the differences in
%mm energetics between each source, particularly the poor coupling of AGB winds to the ISM.
    source energetics and source locations, particularly the higher chance compared to massive stars for AGB stars to eject material into cold gas.
Nearly all of the produced metals are ejected from the galaxy (only 4\% are retained), but metals dominated by AGB enrichment are retained at a fraction of 20\%. In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread compared to elements synthesized in either core collapse or Type Ia supernovae. We discuss the observational implications of these results, their potential use in developing improved models of galactic chemical evolution, and their generalization to more massive galaxies.
\end{abstract}

@@

%The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain. We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (HIM T$\ge 10^{5.5}$~K), and locked in stars (yellow). Again, with the exception of H and He, we only consider metals produced self-consistently through our star formation and stellar feedback methods; the initial mass of each metal species is zero.

%We find two major results. First, nearly all of the metals reside within neutral gas, mostly in the CNM; only a few percent reside in the hot phases. The exact fraction varies with each species, most notably for carbon; these fluctuations are at most $\sim 10$\%. This is not surprising, as the cold phases represent the majority of the mass in the ISM, but, as shown in Section~\ref{sec:statistics}, even though the cold phases harbor most of the metals, the hot phases have significantly higher metal mass fractions. Second, only a small fraction of produced metals are retained within the dwarf galaxy, in agreement with observations of nearby dwarf galaxies \citep[see][]{Kirby2011-metals, McQuinn2015}; however, the retention factor varies. The top panel shows a qualitative disagreement between the retention fractions of N and Ba (about 20\% for each) as compared to the rest of the metals ($\sim$ 4 -- 5\%). This suggests that individual metals \textit{do not} share the same dynamical evolution. Clearly, metal enrichment in galaxies is a phenomenon that cannot be fully captured using single, global metallicity field. In this particular case, assuming that all metals behave the same would underestimate the N and Ba enrichment by a factor of up to five, at least for low mass dwarf galaxies.
%mm [end of apparently deleted section] >>>>>>> 134a2fabac2aea2275cb3e8014308282b438742f

@@

%mm [you could cut this if you want.]
%It is worth noting that this PDF shows the rather small cold gas 
%     fraction found in these models in comparison to the Milky Way
%      ISM, where roughly half the mass is found in cold gas 
%      \citep{Ferriere2001}.
Finally, \cite{Hopkins2013} suggests a different functional form for describing these PDFs across a range of idealized simulations, but it still may be insufficient to fully describe the density PDF in realistic galaxy simulations. Clearly, we are far from a general understanding of mass-weighted and volume-weighted density PDFs in the case of a turbulent, self-gravitating, multi-phase ISM.
